### 2023-11-21 main.tex
''

@@

Should we say that or can we restrict to the case where $\alpha_{a}^{x}=\alpha_{a}$... Maybe we put a remark.\\

>>>>

\begin{remark}[Should we add this?]

@@

		Should we say that or can we restrict to the case where $\alpha_{a}^{x}=\alpha_{a}$?
		 Maybe we put a remark. It does not affect duality, since the matrix $R$ that we define in Section \ref{sectionDuality} does not depend on the density of the multinomials.
